\documentclass[]{manoj-resume}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Manoj}{Uppala}{ \urlstyle{same}\href{https://manojuppala.com}{manojuppala.com} | \href{mailto:uppala0863@gmail.com}{uppala0863@gmail.com}\\
Visakhapatnam, India | 891.976.193 | \href{mailto:uppala.11810921@lpu.in}{uppala.11810921@lpu.in}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Lovely Professional}
\subsection{University}
\descript{BTech in Computer Science}
\location{May 2022 | Punjab, India}
\location{Major: Computer Science}
\location{Minor: Data Science}
Electives: Big Data, Artificial Intelligence
\location{ Cum. GPA: 8.88 / 10}
\sectionsep

\subsection{Narayana IIT academy}
\descript{Senior Secondary Education}
\location{Course work: Maths, Physics and Chemistry}
\location{Grade: 85\%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/manojuppala}{\bf manojuppala} \\
LinkedIn://  \href{https://www.linkedin.com/in/manojuppala/}{\bf manojuppala} \\
YouTube://  \href{https://youtube.com/@manojuppala}{\bf @manojuppala} \\
Stackoverflow://  \href{https://stackoverflow.com/users/11874811/manoj}{\bf manoj} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\subsection{Undergraduate}
Data structures \\
Design and analysis of Algorithms \\
Operating Systems \\
Computer Networks \\
Artificial Intelligence \\
R Programming \\
Big Data Processing Frameworks \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Javascript \textbullet{}   React \textbullet{} Nextjs \textbullet{} Typescript \\ 
MaterialUI \textbullet{} Graphql \textbullet{} Python \textbullet{}  Flask \\ 
Shell  \textbullet{} \LaTeX\ \textbullet{} CSS \textbullet{} HTML \textbullet{} Bootstrap\\ 
\location{Over 1000 lines:}
C \textbullet{} C++ \textbullet{} Java \textbullet{} R \\
\location{Familiar:}
Android studio \textbullet{} React Native \textbullet{} Postgres \\
 MySQL \textbullet{} Scala \textbullet{} Hadoop \textbullet{} Tableau
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     HACKATHONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Hackathons}
\textbullet{} Secured 240/240 in CODEWARS 2k19, by Coding Ninjas. \\
\textbullet{} Code Bake (Hackathon) - Microsoft student partners.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Syscloud}
\descript{| Software Engineer }
\location{Aug 2022 – Dec 2022 | Chennai, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Collaborated and interacted with the Product Managers.
\item Planned and managed multiple parallel projects.
\item Core contributor to a react component library project built upon Material UI and Typescript.
\item Experienced in Configuration driven UI development.
\item Wrote scalable automation tests using cypress. 
\end{tightemize}
\sectionsep

\section{Internships}

\runsubsection{Syscloud}
\descript{| Software Engineer Intern }
\location{Sep 2021 – Jul 2022 | Remote}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Part of UI Engineering team. Extensively worked with React, Typescript, Material UI and graphql. 
\item Hands on experience with Jest, JSdoc, eslint and cypress(for automation testing).
\end{tightemize}
\sectionsep

\runsubsection{Ineuron}
\descript{| Project Intern }
\location{May 2021 – Aug 2021 | Remote Internship}
\begin{tightemize}
\item Part of food recommendation project, a machine learning application to suggest diet plans to users.
\item Contributed to backend development using Django and mongodb.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Swiggy react clone}
\descript{| \href{https://github.com/manojuppala/swiggy}{GitHub}}
\location{Aug 2022 – Sep 2022}
A food ordering website similar to swiggy built using Reactjs, Material UI and Postgres. Performs actions like adding food to cart, placing order and showing order status.  
\sectionsep

\runsubsection{Tasklist-cli}
\descript{| \href{https://github.com/manojuppala/tasklist-cli}{GitHub}}
\location{Mar 2022 – Apr 2022}
Tasklist-cli is a simple and elegant command line application built using Typescript to manage tasks and todos. Tasklist-cli exists to bring all the needed functionalities for simple project management to the terminal.  
\sectionsep

\runsubsection{Sorting algo visualizer}
\descript{| \href{https://github.com/manojuppala/sorting-algorithm-visualizer}{GitHub}}
\location{June 2021 – July 2021}
Python application to visualize various sorting algorithms and their complexities. Built using tkinter GUI in python.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications} 
\begin{tabular}{rll}

2021 & 3 star  & (1600 - 1799) rating on codechef\\
2021 & - & Machine learning masters with deep learning INEURON\\
2020 & - & Geeksforgeeks DSA certification\\
2019 & 5 star & Rating on Hacker Rank(Python, Problem Solving)\\
2019 & Elite  & Programming data structures and algorithms in python - NPTEL\\
2018 & Elite & Programming in C++ - NPTEL \\

\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
